Paper changepoint

### 2019-01-08 paper-comparison/paper_changepoint.Rmd
table summarizing cpt outcomes

@@

@@

>>>>

cpt_dates <- vector(length = 4)
cpt_dates[1] <- mean(df_4[df_4$variable=='V1','value']) %>% date_decimal() %>% format('%d-%m-%Y')
cpt_dates[2] <-mean(df_4[df_4$variable=='V2','value']) %>% date_decimal() %>% format('%d-%m-%Y')
cpt_dates[3] <-mean(df_4[df_4$variable=='V3','value']) %>% date_decimal() %>% format('%d-%m-%Y')
cpt_dates[4] <-mean(df_4[df_4$variable=='V4','value']) %>% date_decimal() %>% format('%d-%m-%Y')

cpt_dates <- as.data.frame(cpt_dates)
write.csv(cpt_dates, 'ldats_paper_dates.csv')

@@

# find means on each changepoint:

@@

cpt_dates <- vector(length = 4)
cpt_dates[1] <- mean(df_4[df_4$variable=='V1','value']) %>% date_decimal() %>% format('%d-%m-%Y')
cpt_dates[2] <-mean(df_4[df_4$variable=='V2','value']) %>% date_decimal() %>% format('%d-%m-%Y')
cpt_dates[3] <-mean(df_4[df_4$variable=='V3','value']) %>% date_decimal() %>% format('%d-%m-%Y')
cpt_dates[4] <-mean(df_4[df_4$variable=='V4','value']) %>% date_decimal() %>% format('%d-%m-%Y')

cpt_dates <- as.data.frame(cpt_dates)
write.csv(cpt_dates, 'paper_paper_dates.csv')
